%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \vspace{-90pt}
    {\Huge \scshape Siddhant Dembi} \\
    % \vspace{29pt}
        \href{https://dembi.xyz/}{\raisebox{-0.2\height}\faUser\ 
        \underline{\textcolor{blue}{dembi.xyz}}} 
        \href{mailto:siddhantdembi@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{\textcolor{blue}{siddhantdembi@gmail.com}}} 
        \href{https://www.linkedin.com/in/siddhantdembi}{\raisebox{-0.2\height}\faLinkedin\ \underline{\textcolor{blue}{/siddhantdembi}}} 
        \href{https://github.com/SiddhantDembi}{\raisebox{-0.2\height}\faGithub\ \underline{\textcolor{blue}{/siddhantdembi}}} 
        \href{tel:+91 8850003687}{\raisebox{-0.2\height}\faPhone\  \underline{\textcolor{blue}{+91 8850003687}}} 
        \href{https://www.google.com/maps/search/?api=1&query=Mumbai}{\raisebox{-0.2\height}{\faHome}\  \underline{\textcolor{blue}{Mumbai}}}
    \vspace{-10pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Engineering in Information Technology (University of Mumbai)}{\textit{2025}}{Thadomal Shahani Engineering College}
      {8.02 CGPA}
  \resumeSubHeadingListEnd
  \vspace{-10pt}

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ford Motors}{\textit{June 2024 - July 2024}}
      {Frontend Developer Intern}{Chennai (2 Months Onsite)}
      \resumeItemListStart
        \resumeItem{Developed a 3D car configurator with \textbf{Three.js} and \textbf{Next.js}, supporting \textbf{450,000} unique configurations}
        \resumeItem{Optimized state management with \textbf{Custom Hooks} and \textbf{Context API}; boosted speed by \textbf{30\%} and cut bugs by \textbf{20\%.}}
        \resumeItem{Designed responsive and aesthetically pleasing UI with \textbf{Tailwind CSS}, and manipulated 3D models using \textbf{Blender}.}
        \resumeItem{Containerized the project with \textbf{Docker}, ensuring consistent functionality and reducing deployment issues by \textbf{40\%.}}
      \resumeItemListEnd
    \vspace{-3pt}

    \resumeSubheading
      {Entelligentsia}{\textit{December 2023 - December 2023}}
      {Backend Developer Intern}{Pune (1 Month Remote)}
      \resumeItemListStart
        \resumeItem{Built \textbf{Serverless} APIs with \textbf{AWS Lambda} in \textbf{Python}, integrated with \textbf{DynamoDB}, deploying \textbf{5} APIs using \textbf{2} tables.}
        \vspace{-12pt}
        \resumeItem{Set up \textbf{JWT} authentication, used \textbf{Regex} for validation across \textbf{5} endpoints, and employed \textbf{YAML} with Serverless.}
        \resumeItem{Created \textbf{RESTful APIs} and achieved \textbf{90\%} test coverage with \textbf{Unit Testing}.}
      \resumeItemListEnd
    \vspace{-3pt}

    \resumeSubheading
      {Decimal Point Analytics}{\textit{May 2023 - July 2023}}
      {Research Analyst Intern}{Mumbai (2 Months Remote)}
      \resumeItemListStart
        \resumeItem{Used \textbf{Streamlit} for web apps to automate Data Cleaning, cutting prep time by \textbf{30\%} and boosting efficiency.}
        \resumeItem{Completed a Coursera course on \textbf{PySpark}, used it with \textbf{Databricks} to clean CSV data, reducing prep time by \textbf{30\%.}}
        \resumeItem{Explored \textbf{Milvus Vector Database}, implemented code samples, and presented the knowledge to \textbf{10} team members.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-12pt}


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={\textbullet}]
    \item \textbf{Programming Languages:} Python, Javascript, Typescript, Java, C, C++.
    \vspace{-8pt}
    \item \textbf{Web Development:} {React.js, Next.js, Three.js, Flask, HTML5, CSS3, TailwindCSS, Bootstrap, Vercel, Render.}
    \vspace{-21pt}
    \item \textbf{Developer Tools:} Git, Github, Postman, AWS (EC2, S3, Lambda), Linux Bash, Docker.
    \vspace{-8pt}
    \item \textbf{Analytics:} Pandas, PySpark, Matplotlib, Numpy, Excel, PowerBI, Tableau.
    \vspace{-8pt}
    \item \textbf{Frameworks/Libraries:} Serverless, Streamlit, Unittest, Regex.
    \vspace{-8pt}
    \item \textbf{Databases:} MySQL, SQLite, MongoDB, DynamoDB, Milvus (Vector Database).
    \vspace{-8pt}
    \item \textbf{Networking and Homelab:} Port Forwarding, DHCP reservation, custom DNS configuration, nmap, SSH, Raspberrypi, Pihole, CasaOS, Portainer, Jellyfin, Nextcloud, Samba NAS, Netdata.
    \vspace{-8pt}
    \item \textbf{Design:} Adobe Photoshop, Adobe Illustrator, Adobe AfterEffects, Adobe Premiere Pro, Blender, Canva.
\end{itemize}
\vspace{-15pt}



%-----------PROJECTS-----------
\section{Projects \href{https://dembi.xyz/project}{\textcolor{blue}{(Other Projects)}}}

\vspace{-8pt}
\resumeSubHeadingListStart

    \resumeProjectHeading
    {\textbf{3D Car Configurator} $|$ \emph{Next.js, Three.js TailwindCSS, Blender, Docker}}{\textit{June 2024}}
    \resumeItemListStart
        \resumeItem{
            This project is a \textbf{Next.js} and \textbf{Three.js} based car customization application that allows users to customize various aspects of a car, such as body color, seat color, interior color, glass type, steering wheel color, tire color, backlight color, and tailwing color. The 3D model renders all the changes live.
        }
        \vspace{-2pt}
        \resumeItem{
             \href{https://3d-car-configurator-beta.vercel.app/}{\textcolor{blue}{\underline{Live Deployment}}}
             \hspace{20pt}
             \href{https://github.com/SiddhantDembi/3d-car-configurator}{\textcolor{blue}{\underline{Source Code}}}
        }
        
    \resumeItemListEnd 
    \vspace{-16pt}
          
    \resumeProjectHeading
    {\textbf{Data Cleaner and Timestamp Analysis} $|$ \emph{Python (Streamlit)}}{\textit{February 2024}}
    \resumeItemListStart
        \resumeItem{
            The project offers a user-friendly interface for cleaning and processing tabular data files (CSV, XLS, XLSX), allowing users to perform various operations on their data such as: \textbf{Replace Null Values, Remove Duplicate Rows, Remove Missing Values, Convert to Lowercase, Delete Columns, Sort Column, and Capitalize Columns.}
        }
        \resumeItem{
            The Timestamp Management application allows users to interact with a \textbf{MySQL} database to manage timestamp entries securely. Users can Save Date and Time, Delete the Latest Entry, and View Previous Entries.
        }
        \vspace{-2pt}
        \resumeItem{
        \href{https://webproject.streamlit.app/}{\textcolor{blue}{\underline{Live Deployment}}}
        \hspace{20pt}
             \href{https://github.com/SiddhantDembi/streamlit-projects}{\textcolor{blue}{\underline{Source Code}}}
        }
       
    \resumeItemListEnd
    \vspace{-3pt}
\resumeSubHeadingListEnd




%-----------INVOLVEMENT---------------
\section{Extracurricular}
\resumeSubHeadingListStart

    \resumeSubheading
    {TSEC Hackathon}{\textit{October 2023}}
    {24 Hour Hackathon}{Thadomal Shahani Engineering College}
    \vspace{-3pt}

    \resumeSubheading
    {SFIT Hackathon}{\textit{March 2023}}
    {24 Hour Hackathon}{St. Francis Institute of Technology}
    \vspace{-3pt}

    \resumeSubheading
    {IETE-TSEC}{\textit{July 2022 - May 2023}}
    {Junior Committee Member}{Design Team}
    \resumeItemListStart
    \resumeItemListEnd
    \vspace{5pt}
    \textbf{Interests and Hobbies:} Fitness, Photography, Travelling, Music

\resumeSubHeadingListEnd
\end{document}
